Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-01-11 eswc-2012/phdsymp.tex
long term goal
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@57 43ef1190-90fd-4dd7-a769-d0121f02b80e
uncommon hypothesis test
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@58 43ef1190-90fd-4dd7-a769-d0121f02b80e

@@

The problems addressed by these studies are almost orthogonal to the
problems considered by my proposed project. I have not to date seen
any work towards using contemporary statistical methods to evaluate
the performance of software, but I shall admit that my literature
study have been limited to RDF/OWL databases, and practical benchmarks
of databases, file systems, scientific software, etc. Thus, the
existence of relevant references in the deeper computer science
literature is a key issue I would appreciate discussing at the
Symposium.

>>>>

I am still in an early phase of my work, and I have not yet started to
explore the scientific literature around SPARQL Federation to any
depth, currently focusing my efforts on benchmarking. Therefore, this
paper also focuses on benchmarking rather than the more long-term goal
of SPARQL Federation.

@@

The problems addressed by these studies are almost orthogonal to the
problems considered by my proposed project. While I have heard of some
cases where a hypothesis test is used to demonstrate that one
implementation is better than another, it is seemingly not common
practice. Furthermore, I have not to date seen any work towards using
contemporary statistical methods to evaluate the performance of
software, but I shall admit that my literature study have been limited
to RDF/OWL databases, and practical benchmarks of databases, file
systems, scientific software, etc. Thus, the existence of relevant
references in the deeper computer science literature is a key issue I
would appreciate discussing at the Symposium.
